---
title: "Scapegoat"
author: "Ada"
format: html
editor: visual
---

## Main Statistical Analyses

```{r}
# Cleaning the environment
rm(list = ls())
gc()
```

```{r}
library(tidyverse)
```

```{r}
df <- read.csv("clean_data.csv")
df
```

```{r}
# Recode ineligible responsibility attributions as "No" responsibility attributions
df_recoded <- df %>%
  mutate(Attribution_Presence = case_when(
    Sender_Relevance == 0 ~ 0,
    is.na(Evaluation) ~ 0,
    is.na(Topic) ~ 0,
    TRUE ~ Attribution_Presence
  ))

# Recode other columns with NAs when there is "No" responsibility attributions
df_recoded <- df_recoded %>%
  mutate(across(
    .cols = -c(Attribution_Presence, Time_Stamp, Text, Date, Post_ID), # except these columns
    .fns = ~ ifelse(Attribution_Presence == 0, NA, .)
  ))

df_recoded
```

**RQ1a: To what extent does the proportion of posts containing responsibility attributions for voting issues vary?**

```{r}
# Identify posts instead of individual responsibility attributions
df_unique <- df_recoded %>%
  group_by(Post_ID) %>%
  summarise(Attribution_Presence = as.integer(any(Attribution_Presence == 1)), Time_Stamp = unique(Time_Stamp))

print(df_unique)

# Step 1: Creating a contingency table
contingency_table_1a <- table(df_unique$Time_Stamp, df_unique$Attribution_Presence)
contingency_table_1a

# Step 2: Applying the chi-square test function
chi_square_test_1a <- chisq.test(contingency_table_1a)
chi_square_test_1a
```

**RQ1b: To what extent does the proportion of responsibility attribution evaluations vary?**

```{r}
# Step 1: Creating a contingency table
contingency_table_1b <- table(df_recoded$Time_Stamp, df_recoded$Evaluation)
contingency_table_1b

# Step 2: Applying the chi-square test function
chi_square_test_1b <- chisq.test(contingency_table_1b)
chi_square_test_1b
```

**RQ4a:** **To what extent does the proportional distribution of targets for positive responsibility attributions vary?**

```{r}
# Filter the df with positive responsibility attributions only
df_positive <- df_recoded %>% 
  filter(Evaluation == 1)

# Step 1: Creating a contingency table
contingency_table_4a <- table(df_positive$Time_Stamp, df_positive$Target)
contingency_table_4a

# Step 2: Applying the fisher test function
fisher_test_4a <- fisher.test(contingency_table_4a)
fisher_test_4a
```

**RQ4b:** **To what extent does the proportional distribution of targets for negative responsibility attributions vary?**

```{r}
# Filter the df with negative responsibility attributions only
df_negative <- df_recoded %>% 
  filter(Evaluation == 0)

# Step 1: Creating a contingency table
contingency_table_4b <- table(df_negative$Time_Stamp, df_negative$Target)
contingency_table_4b

# Step 2: Applying the chi-square test function
chi_square_test_4b <- chisq.test(contingency_table_4b)
chi_square_test_4b
```

**RQ5a: To what extent does the proportional distribution of voting issues for positive responsibility attributions vary?**

```{r}
# Filter the df with positive responsibility attributions only
df_positive <- df_recoded %>% 
  filter(Evaluation == 1)

# Step 1: Creating a contingency table
contingency_table_5a <- table(df_positive$Time_Stamp, df_positive$Topic)
contingency_table_5a

# Step 2: Applying the fisher test function
fisher_test_5a <- fisher.test(contingency_table_5a)
fisher_test_5a
```

**RQ5b: To what extent does the proportional distribution of voting issues for negative responsibility attributions vary?**

```{r}
# Filter the df with negative responsibility attributions only
df_negative <- df_recoded %>% 
  filter(Evaluation == 0)

# Step 1: Creating a contingency table
contingency_table_5b <- table(df_negative$Time_Stamp, df_negative$Topic)
contingency_table_5b

# Step 2: Applying the fisher test function
fisher_test_5b <- fisher.test(contingency_table_5b)
fisher_test_5b
```
